%!TEX program = xelatex
%==============================================================================
%                    JESS SULLIVAN — RESUME
%==============================================================================
% Compile with XeLaTeX for modern font support
% Run twice for proper cross-references
%==============================================================================

\documentclass[10pt,letterpaper]{article}

%------------------------------------------------------------------------------
% PACKAGES
%------------------------------------------------------------------------------
\PassOptionsToPackage{hyphens}{url}
\usepackage[margin=0.65in, top=0.5in, bottom=0.6in]{geometry}
\usepackage{fontspec}
\usepackage{titlesec}
\usepackage{titletoc}
\usepackage{hyperref}
\usepackage{xurl}
\setlength{\emergencystretch}{2em}
\Urlmuskip=0mu plus 1mu\relax
\usepackage{xcolor}
\usepackage{enumitem}
\usepackage{fancyhdr}
\usepackage{lastpage}
\usepackage{microtype}
\usepackage{graphicx}
\usepackage{multicol}
\usepackage{bookmark}
\usepackage{calc}
\usepackage{tikz}
\usepackage{tabularx}
\usepackage{colortbl}
\usepackage{setspace}

%------------------------------------------------------------------------------
% COLOR PALETTE
%------------------------------------------------------------------------------
\definecolor{primary}{HTML}{1a365d}
\definecolor{secondary}{HTML}{2c5282}
\definecolor{accent}{HTML}{3182ce}
\definecolor{muted}{HTML}{4a5568}
\definecolor{light}{HTML}{e2e8f0}
\definecolor{linkcolor}{HTML}{2b6cb0}

%------------------------------------------------------------------------------
% FONTS
%------------------------------------------------------------------------------
% Use Tectonic bundle filenames so builds do not depend on OS font registration.
\setmainfont{lmroman10-regular.otf}[
    BoldFont=lmroman10-bold.otf,
    ItalicFont=lmroman10-italic.otf,
    BoldItalicFont=lmroman10-bolditalic.otf
]
\setsansfont{lmsans10-regular.otf}[
    BoldFont=lmsans10-bold.otf,
    ItalicFont=lmsans10-oblique.otf,
    BoldItalicFont=lmsans10-boldoblique.otf
]
\setmonofont{lmmono10-regular.otf}[
    BoldFont=lmmonolt10-bold.otf,
    ItalicFont=lmmono10-italic.otf,
    BoldItalicFont=lmmonolt10-boldoblique.otf
]

%------------------------------------------------------------------------------
% HYPERREF CONFIGURATION
%------------------------------------------------------------------------------
\hypersetup{
    colorlinks=true,
    linkcolor=primary,
    urlcolor=linkcolor,
    citecolor=secondary,
    bookmarksnumbered=true,
    bookmarksopen=true,
    bookmarksopenlevel=1,
    pdfauthor={Jess Sullivan},
    pdftitle={Jess Sullivan — Resume},
    pdfsubject={Full Stack Engineer, DevSecOps, ML/HPC},
    pdfkeywords={DevSecOps, Machine Learning, Full Stack, HPC, Chapel, Haskell, SvelteKit},
    pdfstartview={FitH},
    pdfpagemode={UseOutlines}
}

%------------------------------------------------------------------------------
% HEADER & FOOTER
%------------------------------------------------------------------------------
\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\fancyfoot[C]{\small\color{muted} Jess Sullivan \quad$\cdot$\quad Page \thepage\ of \pageref{LastPage}}

%------------------------------------------------------------------------------
% SECTION FORMATTING
%------------------------------------------------------------------------------
\titleformat{\section}
    {\Large\bfseries\sffamily\color{primary}}
    {}
    {0em}
    {}
    [\vspace{-0.5em}\textcolor{accent}{\rule{\linewidth}{1.5pt}}]

\titleformat{\subsection}
    {\large\bfseries\sffamily\color{secondary}}
    {}
    {0em}
    {}

\titleformat{\subsubsection}
    {\normalsize\bfseries\color{muted}}
    {}
    {0em}
    {}

\titlespacing*{\section}{0pt}{1.2em}{0.6em}
\titlespacing*{\subsection}{0pt}{0.8em}{0.4em}
\titlespacing*{\subsubsection}{0pt}{0.6em}{0.2em}

%------------------------------------------------------------------------------
% LIST FORMATTING
%------------------------------------------------------------------------------
\setlist[itemize]{
    leftmargin=1.5em,
    itemsep=0.15em,
    parsep=0em,
    topsep=0.25em,
    label={\textcolor{accent}{\textbullet}}
}

%------------------------------------------------------------------------------
% CUSTOM COMMANDS
%------------------------------------------------------------------------------
\newcommand{\role}[2]{%
    \noindent\textbf{\color{secondary}#1} \hfill \textit{\color{muted}(#2)}\par\vspace{0.3em}
}

\newcommand{\tech}[1]{\texttt{\small\color{secondary}#1}}
\newcommand{\cvlink}[2]{\href{#1}{\color{linkcolor}#2}}
\newcommand{\shadowlink}[2]{\href{#1}{\textcolor{black}{#2}}}

%------------------------------------------------------------------------------
% DOCUMENT START
%------------------------------------------------------------------------------
\begin{document}

%==============================================================================
% HEADER
%==============================================================================
\begin{center}
    \begin{tikzpicture}
        \fill[primary] (0,0) rectangle (\textwidth, 0.12);
    \end{tikzpicture}
    
    \vspace{0.4em}
    
    {\Huge\bfseries\sffamily\color{primary} Jess Sullivan}
    
    \vspace{0.4em}
    
    {\color{muted} Full Stack Engineer \quad$\cdot$\quad DevSecOps \quad$\cdot$\quad Computer Vision \quad$\cdot$\quad Kernel \& Security Research \quad$\cdot$\quad ML/HPC}
    
    \vspace{0.4em}
    
    {\small\color{secondary} Lewiston, ME \& Boston, MA \quad$\cdot$\quad 617-795-6912 \quad$\cdot$\quad \href{mailto:jess@sulliwood.org}{jess@sulliwood.org} \quad$\cdot$\quad \href{https://github.com/jesssullivan}{github.com/jesssullivan}}
    
    \vspace{0.2em}
    
    {\small\color{secondary} \href{https://transscendsurvival.org}{transscendsurvival.org} \quad$\cdot$\quad \href{https://www.linkedin.com/in/jess-sullivan-11032a367/}{LinkedIn}}
    
    \vspace{0.4em}
    \begin{tikzpicture}
        \fill[accent] (0,0) rectangle (\textwidth, 0.06);
    \end{tikzpicture}
\end{center}

\vspace{0.3em}

%==============================================================================
% CORE COMPETENCIES
%==============================================================================
\vspace{-0.3em}
\begin{center}
\footnotesize
\begin{tabular}{@{}l@{\hspace{1em}}l@{\hspace{1em}}l@{\hspace{1em}}l@{}}
\textbf{\color{secondary}Languages} & \textbf{\color{secondary}Web \& Product} & \textbf{\color{secondary}Systems \& Security} & \textbf{\color{secondary}Infrastructure} \\[0.2em]
Python, TypeScript    & \shadowlink{https://svelte.dev/docs/svelte/what-are-runes}{SvelteKit Runes}, Bun       & \shadowlink{https://ghidra-sre.org/}{GhidraScript}, Frida                                  & Nix flakes, \shadowlink{https://bazel.build/remote/rbe}{Bazel RBE} \\
Rust, Zig             & \shadowlink{https://vite.dev/rolldown}{Vite 8/Rolldown}, TS7                           & Zig ABI/FFI, ILSpy                                                                        & OpenTofu, sops+age \\
Chapel, Haskell       & Auth, scheduling, mapping, telemetry                                                    & SAML, OAuth, YubiKey                                                                      & Ansible, RKE2 \\
Go, C++, R, fish      & Postgres, Tempo/Grafana                                                                 & Caddy, KeePassXC/kdbx                                                                     & Podman Compose, \shadowlink{https://tailscale.com/kb/1236/kubernetes-operator}{Tailscale Operator} \\
\end{tabular}
\end{center}

\vspace{0.1em}

%==============================================================================
% TECHNICAL RESUME
%==============================================================================
\section{Experience}
\label{sec:resume}

%--- Full Stack Contracting & FOSS ---
\role{Full Stack Contracting and FOSS}{Ongoing}

Ongoing contributor and community member of numerous open source projects including---and not limited to---the \textbf{Apache Foundation}, \cvlink{https://github.com/rspamd/rspamd/pull/5923}{\textbf{rspamd}}, \cvlink{https://github.com/chapel-lang/mason-registry/pull/77}{\textbf{Chapel-lang}}, \cvlink{https://github.com/numtide/nix-vm-test/pull/172}{\textbf{numtide}/nix-vm-test}, \cvlink{https://github.com/manaflow-ai/cmux/pull/1877}{\textbf{manaflow-ai}/cmux}, \cvlink{https://github.com/diku-dk/futhark/pull/2365}{\textbf{diku-dk}/Futhark}, \cvlink{https://github.com/caddyserver/xcaddy/pull/238}{\textbf{xCaddy}}, \textbf{libdns}, Skeleton UI, \textbf{Klipper}, \textbf{Joplin}, \cvlink{https://github.com/indutny/fft.js}{\textbf{FFT.js}}, \textbf{KeePassXC}, \cvlink{https://github.com/ciscoheat/sveltekit-superforms/pull/678}{svelte-superforms}, \cvlink{https://github.com/shikijs/shiki}{\textbf{ShikiJS}}, \cvlink{https://github.com/tidyverse/ggplot2}{\textbf{ggplot2}}, the \textbf{Rocky Enterprise Linux Foundation}, \textbf{Liqo}, \textbf{Budgie DE}, \cvlink{https://github.com/Jesssullivan/quickchpl}{\textbf{Mason}}, along with authoring numerous FOSS automation tools, libraries and open source utilities. Expanded client list and customer references available upon request.

\begin{itemize}
    \item Startup work: \textbf{Dover Micro} (2017), \textbf{Adaptive Motorsport} (2018)
    \item Web GIS tools for \textbf{National Park Service}, \textbf{Foundation for Healthy Communities}, \textbf{GPRED}, \textbf{Northern Border Regional Commission}. Presented at 2019 \textbf{AAG Annual Meeting} in Washington, DC (\S\ref{sec:publications}).
    \item Fine-grained image classification with \textbf{MushroomObserver.org} and \textbf{Visipedia}; early adopter of CNN-based species ID at scale.
\end{itemize}

\vspace{0.4em}
\noindent\textit{\color{muted}Current stack:}
\begin{itemize}
    \item \textbf{Web \& product systems:} \tech{SvelteKit} Runes, \tech{Bun}, \tech{Vite 8} (Rolldown), TS7; auth, scheduling, mapping, telemetry, and site systems without package-level public coupling.
    \item \textbf{Infrastructure \& platform:} \tech{Nix} flakes, \tech{Bazel RBE}, justfile, \tech{OpenTofu}, sops+age, \tech{Ansible}, \tech{Postgres}, Podman Compose, on-prem \tech{RKE2}, Tailscale Operator, \tech{Caddy}, Tempo/Grafana.
    \item \textbf{Systems, HPC \& reverse engineering:} \tech{Chapel}, \tech{Rust}, \tech{Zig} for ABI/FFI work, \tech{Haskell}, \tech{GhidraScript}, \tech{Ghidra}, \tech{Frida}; performance systems, property-based testing, and binary analysis.
\end{itemize}
\noindent\textit{\color{muted}Daily operating environment:} fish shell, direnv, YubiKey, KeePassXC/kdbx, Linear, macOS teletype workstation, Rocky Linux daily-driver, and personal SearXNG/search/indexing/MCP research tooling.

\vspace{0.3em}
\noindent\textit{\color{muted}Research:}
\begin{itemize}
    \item \textbf{Reverse Engineering \& Binary Analysis:} \tech{GhidraScript}, \tech{Frida}, \tech{ILSpy}, Mitre \cvlink{https://github.com/Jesssullivan/caldera}{Caldera}, \tech{Zig}. Firmware RE and \cvlink{https://github.com/Jesssullivan/hiberpower-ntfs/pull/1}{NVMe XRAM recovery} (see \S\ref{sec:publications}).
    \item \textbf{Author of numerous Zig capability libraries} with C ABI surfaces: \cvlink{https://github.com/Jesssullivan/zig-crypto}{\tech{zig-crypto}} (\cvlink{https://transscendsurvival.org/zig-crypto/}{docs}), \cvlink{https://github.com/Jesssullivan/zig-notify}{\tech{zig-notify}} (\cvlink{https://transscendsurvival.org/zig-notify/}{docs}), \cvlink{https://github.com/Jesssullivan/zig-keychain}{\tech{zig-keychain}} (\cvlink{https://transscendsurvival.org/zig-keychain/}{docs}), \cvlink{https://github.com/Jesssullivan/zig-ctap2}{\tech{zig-ctap2}} (\cvlink{https://transscendsurvival.org/zig-ctap2/}{docs}).
    \item \cvlink{https://github.com/tinyland-inc/linux-xr}{\textbf{linux-xr}} --- Rocky Linux 10 RPM kernel lane carrying XR display patches and \cvlink{https://github.com/tinyland-inc/linux-xr/pull/66}{Dirty Frag security backports}. Backported \textbf{CVE-2026-31431}, \textbf{CVE-2026-43284}, and \textbf{CVE-2026-43500} into 6.1.y ahead of public disclosure.
    \item \textbf{Heterogeneous Compute:} \tech{WebGPU}, \tech{Futhark} (GPU-targeting functional language), deeper WASM integration and WASM-native inference pipelines.
    \item \textbf{Functional Programming:} ESDT Monads and pixelwise classification research (\cvlink{https://github.com/Jesssullivan/pixelwise-research}{pixelwise-research}). \tech{Rust} (SIMD), \tech{Nix} (build systems), and everyday \tech{Chapel}/\tech{Rust}/\tech{Zig} systems work.
\end{itemize}

\vspace{0.4em}

%--- Systems Analyst ---
\role{Systems Analyst (DevSecOps) @ Bates College}{2024--Present}

Scalable enterprise systems supporting staff, faculty, and ILS team. Legacy modernization; bespoke Ansible extensions/roles/plugins; 24/7 CVE mitigation; SAML and application interoperability; OpenTelemetry reporting; CI/CD pipelines (GitLab AutoDevOps, OpenTofu, RKE2 + Rancher); leading IaC adoption college-wide.

\subsubsection{Noteworthy projects:}
\begin{itemize}
    \item Developed high performance orchestrator and instrumentation tooling for degree management and degree auditing software in \tech{Haskell} + \tech{Python} (QuickCheck, Cabal, podman-compose for development, FPM for packaging and autodevops for CI/CD); uplifted ``unautomatable'' 1980s morris-worm era code unique to higher ed into a verifiable, traceable, k8s friendly workload
    \item Overhauled and completely automated the lifecycle of our event management system (extensive development in \tech{C\#}, \tech{Go}, \tech{Ansible})
    \item Led adoption of horizontally scalable \tech{Apache Solr} instances for multiple public and private indexing and search applications
    \item Led adoption and built out numerous internal ACME-first certificate management and DNS libraries, templates and tooling
    \item Extensive work and peer education around enterprise secret management patterns and SAML at the college. Developed numerous SAML integrations, LTI integrations, Shibboleth and led adoption of \tech{KeePassXC} as part of a declarative Ansible workflow.
\end{itemize}

\vspace{0.4em}

%--- Tinyland ---
\role{Tinyland, Inc}{2024--Present}

Agent orchestration and source-available infrastructure lifecycle tooling for higher education and lab-scale systems. Current work spans SLM-backed automation, multicloud IaC harnesses, Chapel-based parallelism, and Kubernetes-native research infrastructure.

\vspace{0.4em}

%--- Computer Vision ---
\role{Computer Vision Software Engineer @ Macaulay Library, Cornell Lab of Ornithology}{2018--2022}

Developed \& launched \cvlink{https://merlin.allaboutbirds.org/download/}{\textbf{Merlin Sound ID}}, a production fine-grained audio classification system now used by millions worldwide. Led R\&D on internal ML annotation tooling, model evaluation APIs, and end-to-end MLOps pipelines. Built real-time inference demos deployed at scale.

\vspace{0.4em}
\noindent\textit{\color{muted}Stack:}
\begin{itemize}
    \item \textbf{Model Training:} Python (\tech{TensorFlow}, \tech{NumPy}, \tech{Pandas}, \tech{Matplotlib}, \tech{Jupyter})
    \item \textbf{Web \& Inference:} \tech{Flask}, \tech{TypeScript}, \tech{React}, \tech{Vue}, \tech{Docker}, \tech{WebAssembly}, \tech{React Native}, \tech{Swift}
    \item \textbf{Infrastructure:} EC2, Heroku, BitBucket CI/CD, production model deployment at scale
\end{itemize}

\vspace{0.4em}

%--- Fab Lab ---
\role{Fabrication Laboratory Manager @ Cornell CALS}{2021--2022}

Developed and taught rapid fabrication curricula. \tech{OpenSCAD}, \tech{Fusion 360}, \tech{Inkscape}, \tech{C++}. GitHub/Linear project management.

%==============================================================================
% VOLUNTEER & COMMUNITY
%==============================================================================
\section{Volunteer \& Community}
\label{sec:volunteer}

\role{First Fellow @ D\&M Makerspace, Plymouth State University}{2017--2020}

Taught \textbf{Advanced GIS Programming} \& \textbf{Intro to Electromechanics}. COVID-19 response: coordinated regional makerspace network for medical PPE manufacturing.

\vspace{0.3em}

\role{Membership Chair \& 3D Printing Captain @ Ithaca Generator}{2020--2022}

Led 501(c)(3) makerspace through rapid growth; coached hundreds via ``Fusion 360 for 3D printing'' series.

%==============================================================================
% PUBLICATIONS
%==============================================================================
\section{Publications}
\label{sec:publications}

Reitsma, L.R., Burns, C., \& \textbf{Sullivan, J.} (2019). \textit{Poecile atricapillus} (Black-capped Chickadee) Feeding \textit{Catharus guttatus} (Hermit Thrush) Nestlings. \textit{Northeastern Naturalist}, 26(2). \cvlink{https://doi.org/10.1656/045.026.0213}{doi:10.1656/045.026.0213}

\vspace{0.3em}

\textbf{Sullivan, J.} (2026). Recovering Write-Protected NVMe SSDs Through USB Bridge XRAM Injection: Bypassing the ASMedia ASM2362 Firmware Opcode Whitelist. \cvlink{https://transscendsurvival.org/papers/recovery-paper.pdf}{recovery-paper.pdf}

\vspace{0.4em}
\noindent\textit{\color{muted}Presentations:}

\vspace{0.2em}
\textbf{Sullivan, J.} (2019). Web GIS: Telling Stories \& Solving Problems. \textit{Association of American Geographers Annual Meeting}, Washington, DC.

%==============================================================================
% END
%==============================================================================

\vspace{0.4em}

\begin{center}
    \begin{tikzpicture}
        \fill[primary] (0,0) rectangle (\textwidth, 0.1);
    \end{tikzpicture}
\end{center}

\end{document}
